Project

### 2022-04-03 Project/DraftR.Rmd
Update DraftR.Rmd

```{r}
#ltrsdat$year <- as.factor(ltrsdat$year)
#ltrsdat$transect <- as.factor(ltrsdat$transect)
#ltrsdat$site <- as.factor(ltrsdat$site)
#ltrsdat$treat <- as.factor(ltrsdat$treat)
#ltrsdat$Source <- as.factor(ltrsdat$Source)
#ltrsdat$tbo <- as.factor(ltrsdat$tbo)
```

@@

@@

```{r}
ltrs_pc$PC1 <- ltrsfull$scores[,1]
ltrs_pc$PC2 <- ltrsfull$scores[,2]
ltrs_pc$PC3 <- ltrsfull$scores[,3]
qplot(x = PC1, y = PC2, color = site, facets = "Source", data = ltrs_pc) +
theme_classic()
```

@@

## FAMD
ltrs_fa <- subset(ltrs_pc, 
                   select=-c(PC1, PC2, PC3))

ltrs.famd <- FAMD(ltrs_fa, 
                 sup.var = 11,  ## Set the target variable "totgoodseed" as a supplementary variable
                 graph = FALSE, 
                 ncp=25)

@@

```{r}
#to do factor analysis, we change 'totgoodseed' from numeric variable into catergorical as 'low', 'med', 'high'
ltrs_fa
```

```{r}
## Plot individual observations
fviz_famd_ind(ltrs.famd, label = "none", 
              habillage = "totgoodseed", palette = c("#00AFBB", "#FC4E07"), # color by groups 
              repel = TRUE, alpha.ind = 0.5) + 
  xlim(-5, 6) + ylim (-4.5, 4.5) +
  theme(text = element_text(size=20), axis.text.x = element_text(size=20), axis.text.y = element_text(size=20))
```

>>>>

```{r}
ltrsdat$year <- as.factor(ltrsdat$year)
ltrsdat$transect <- as.factor(ltrsdat$transect)
ltrsdat$site <- as.factor(ltrsdat$site)
ltrsdat$treat <- as.factor(ltrsdat$treat)
ltrsdat$Source <- as.factor(ltrsdat$Source)
ltrsdat$tbo <- as.factor(ltrsdat$tbo)
```

@@

```{r}
ltrs_pc$PC1 <- ltrsfull$scores[,1]
ltrs_pc$PC2 <- ltrsfull$scores[,2]
ltrs_pc$PC3 <- ltrsfull$scores[,3]
```

@@

```{r}
qplot(x = PC1, y = PC2, color = site, facets = "Source", data = ltrs_pc) +
theme_classic()
```

@@

## FAMD
ltrs_fa <- subset(ltrsdat, subset = site %in% c("L", "M", "H"),
                   select=-c(aveseed2, totbadseed))

ltrs_fa <- ltrs_fa %>%
  na.omit()

ltrs.famd <- FAMD(ltrs_fa, 
                 sup.var = 4,  ## Set the target variable "treatment" as a supplementary variable
                 graph = FALSE, 
                 ncp=25)

@@

```{r}
## Plot individual observations
fviz_famd_ind(ltrs.famd, label = "none", 
              habillage = "treat", palette = c("#FC4E07",  "#63d5ff"), # color by groups 
              repel = TRUE, alpha.ind = 0.5) + 
  xlim(-5, 6) + ylim (-4.5, 4.5) +
  theme(text = element_text(size = 15), axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 15))
```
As individuals with similar characteristics (in this case, in terms of plants' before- and after- habitat and reproductive success) are close to each other on the figure, the large overlap between the "OTC" and "TR" populations suggests that if there are significant/meaningful differences between control and warmed groups, they are likely complex and non-linear.
